\documentclass{cvx}
\usepackage{fullpage}
\begin{document}

\name{Eugene Y. Q. Shen}
\dotseptwo{eugene@eyqs.ca}{(604) 295--7569}
\dotsepthree{6098 Commercial Street}{Vancouver, Canada}{V5P 3N9}

\section{Experience}
\datedsubsection{Teaching Assistant}{January 2014--Present}
Undergraduate teaching assistant for APSC 160, Introduction to Computation in Engineering Design.
\begin{itemize}
  \setlength \itemsep{0em}
  \item Mark over 70 C labs every week;
  \item Create and maintain a script to automatically open and compile the labs;
  \item Hold office hours, attend weekly meetings, and mark midterms and the final exam.
\end{itemize}

\datedsubsection{Red Cross HELP Volunteer}{August 2014--September 2015}
Volunteer at the Vancouver depot for the Health Equipment Loan Program of the Canadian Red Cross.
\begin{itemize}
  \setlength \itemsep{0em}
  \item Met with clients at the front desk and processed their loan requests;
  \item Keyed in loan data, organized equipment inventory, and responded to calls.
\end{itemize}


\section{Awards}
\datedsubsection{2nd in Division Two, Pacific Northwest Regionals}{November 2015}
Participated in a team of 3 UBC students for the ACM-ICPC Pac-NW programming competition.
\datedsubsection{4th in the Open Round, North American Computational Linguistics Olympiad}{March 2015}
\datedsubsection{2nd in the Western Division, Canadian Computing Competition}{January 2013}
\vspace{10pt}
\datedsubsection{N. L. Drugge Shield, Sir Winston Churchill Secondary}{June 2015}
One of the six major awards. Awarded to the graduating student that most demonstrates scholastic inquiry.
\datedsubsection{R. A. Pyke Mathematics Memorial Scholarship, Sir Winston Churchill}{June 2015}
Awarded to the graduating student with the strongest affinity for mathematics.


\section{Education}
\datedsubsection{University of British Columbia}{September 2015--Present}
First-year in the Faculty of Applied Sciences, aiming for a degree in Engineering Physics with Minors in Honours Mathematics and Music Composition. Current courses include MUSC 101, MATH 217, CPSC 490.
\datedsubsection{Sir Winston Churchill Secondary}{September 2012--May 2015}
Candidate in the International Baccalaureate program, with a final mark of 41 out of 42 base points.
\end{document}
